Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd

@@

$$ \beta^T = \begin{bmatrix} -0.23198507 & -0.05391226 & 0.26336295 & -0.03586852 \end{bmatrix} $$

@@

@@

## Discussion
The posterior estimates of our model suggest that there is some weak evidence that with increasing temperature, the reproductive number R decreases. The effect of relative humidity on the reproductive number is much less conclusive. As we only used data from Italy in our model building, there is a limited range of weather information than we would like to have. Our model does a good job estimating the reproductive number $R$ in various provinces with high confidence level and provides valuable information for policy makers. However, with no access to line-list data to estimate the serial interval number ourselves, our estimated reproductive number R is limited by the accuracy of the serial interval number we used. The estimated $R$ values tend to have wide confidence interval in the beginning dates due to the imported cases in the beginning and the lack of testing.

>>>>

```{r include=FALSE}
res <- results()
plot_beta_confidence(res)
```

@@

$$ \beta^T = \begin{bmatrix} -0.232 & -0.054 & 0.263 & -0.036 \end{bmatrix} $$

@@

In comparison, the EpiEstim and OLS model produced beta values of:

$$ \beta^T = \begin{bmatrix} -0.051 & -0.045 & -0.081 & -0.051 \end{bmatrix} $$

for temperature, relative humidity, Gross Domestic Product (GDP) and population density, respectively, with $$\beta_0 = 1.08802$$ in the overall model for $R$:

$$
R_i(t) = \exp\left(\beta_0 + \mathbf{\beta}^T x_i(t) + \varepsilon_i(t) \right)
$$

@@

## Discussion

The posterior estimates of our model suggest that there is some weak evidence that with increasing temperature, the reproductive number R decreases. The effect of relative humidity on the reproductive number is much less conclusive. As we only used data from Italy in our model building, there is a limited range of weather information than we would like to have. Our model does a good job estimating the reproductive number $R$ in various provinces with high confidence level and provides valuable information for policy makers. However, with no access to line-list data to estimate the serial interval number ourselves, our estimated reproductive number R is limited by the accuracy of the serial interval number we used. The estimated $R$ values tend to have wide confidence interval in the beginning dates due to the imported cases in the beginning and the lack of testing.
